Pythagorean Theorem

### 2022-02-02 _posts/2022-02-02-pythagorean-theorem/pythagorean-theorem.Rmd
add category

---
title: "Pythagorean Theorem"
description: |
  How did I not know this
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-02
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Pythagorean Theorem"
description: |
  How did I not know this
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-02
output:
  distill::distill_article:
    self_contained: false
categories:
  - math
---
